Rapid Georeferencing n of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle

### 2023-09-30 paper/paper.tex
Updates from Overleaf

For decades, multi-spectral imagers* have seen wide spread adoption in the remote sensing community as a means to take advantage of the wealth of information contained in the reflectance spectra of materials. In addition to the three color filters of traditional cameras, *multi-spectral* imagers, like those deployed on MODIS, Sentinel 2, and other satellite missions, capture many additional features by utilizing wavelength bands ranging from the near-UV, through the visible spectrum, and into the Infrared. With this additional information, multi-spectral remote sensing platforms are able to aid in a variety of domains from tracking land change, characterizing deforestation, monitoring erosion, evaluating crop health, and many others (add references here).

(**add a figure showing the different wavelength bands of publically available satellites**)

@@

>>>>

For decades, multi-spectral imagers have seen wide spread adoption in the remote sensing community as a means to take advantage of the wealth of information contained in the reflectance spectra of materials. In addition to the three color filters of traditional cameras, multi-spectral imagers, like those deployed on MODIS, Landsat, Sentinel 2, and a plethora of other satellite missions, capture many additional features by utilizing wavelength bands ranging from the near-UV, through the visible spectrum, and into the Infrared. With this additional spectral information, multi-spectral remote sensing platforms are able to aid in a variety of domains like vegetation monitoring, land use classification, water quality assessment, smart agriculture, environmental change detection, and disaster management \textbf{(add references)}.

(**add a figure showing the different wavelength bands of publicly available satellites**)
\begin{figure}[H]
    \centering
    \includegraphics[width=12cm]{./assets/passbands.eps}
    \caption{Components of the Autonomous Drone HSI platform.}
    \label{fig:drone-components}
\end{figure}

@@

Make sure to use \textit{nadir-oriented} in description of HSI on the drone.
